\chapter{Requirements}

Listed below are the functional requirements, non-functional requirements, and design constraints of the project as gathered during the Requirements gathering phase. These requirements gave shape to our system and laid out what our system will look like upon completion. The first category of requirements, functional requirements, detail what our system will be able to do. Upon final evaluation, these requirements are either present or they are not, meaning that there is no middle ground and they are easily identifiable. The next category, non-functional requirements, describe how our system will behave. Unlike functional requirements, these requirements are not black-and-white, and are evaluated on a qualitative rather than quantitative scale. This means that these requirements must be more closely evaluated and take into account the feedback from multiple perspectives, including the developer's and the user's perspective. Finally, the design constraints define the technological limitations that our system must adhere to. Design constraints limit the creative freedom the developers have to implement the system based on the constraints they must live within.

\section{Functional Requirements}
Critical:
\begin{itemize}
\item Provide input via the keyboard.
\item Capture audio via device microphone.
\item Speak through device speaker.
\item Suggest responses based on voice input.
\end{itemize}
Recommended:
\begin{itemize}
\item Provide input options via picture cards.
\end{itemize}
Suggested:
\begin{itemize}
\item Say keyword to activate microphone and save battery.
\end{itemize}

\section{Non-Functional Requirements}
Critical:
\begin{itemize}
\item The system will be able to handle multiple users.
\item The system's user interface will be intuitively designed.
\end{itemize}
Recommended:
\begin{itemize}
\item The system will be secure when storing private data.
\end{itemize}
Suggested:
\begin{itemize}
\item The system's user interface will be able to use graphics that are intuitive and familiar.
\item The system will be unaffected in loud environments.
\end{itemize}

\section{Design Constraints}
\begin{itemize}
\item The system must consist of a mobile application that runs on iPad devices.
\end{itemize}